---
title: "Exercise #3"
subtitle: "Fortgeschrittene Statistische Software für NF"
author: "Shuman Mo (12468087)"
date: "`r Sys.Date()`"
output: distill::distill_article
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE, message=FALSE}
library(tidyverse)
library(readr)
library(dplyr)
library(tidyr)
library(stringr)
library(janitor)
library(ggplot2)
```

## Exercise 1: Initializing git

### d) 

-   Strength

**Distributed Version Control**: Git's distributed architecture allows
every user to have a complete copy of the repository, including its full
history. This ensures that work can be done offline and reduces the risk
of data loss since every user has a full backup.

**Branching and Merging**: Git provides powerful branching and merging
capabilities. Branches in Git are lightweight and can be created
quickly, allowing users to experiment and develop features in isolation
from the main codebase.

-   Weaknesses

**Complexity**: Git has a steep learning curve, especially for
beginners. Its command-line interface and the complexity of certain
commands can be daunting.

**Performance with Large Repositories**: While Git handles small to
medium-sized repositories efficiently, it can experience performance
issues with very large repositories or repositories with a large number
of files and long history.

## Exercise 2: Putting your Repository on GitHub

### a) 

https://github.com/MosGalaxy/2024-exeRcise-sheet-3.git

## Exercise 3: Baby-Names in Munich

### b) 

```{r}
# Load data for 2023 and 2022
vornamen_2023 <- read_csv("DATA/vornamen-muenchen-2023.csv")
vornamen_2022 <- read_csv("DATA/open_data_portal_2022.csv")

# Check the type of the "Anzahl" variable for both years
class(vornamen_2023$Anzahl)
class(vornamen_2022$Anzahl)
```

After examining the data, we found that some counts are represented as non-numeric values (e.g., "4 oder weniger"). We can use ifelse to conditionally convert "4 oder weniger" to 4 while keeping other values as numeric. 

Compared to converting to NA, this approach retains the sample size and contextual information associated with the "<= 4" values if necessary.

```{r include=FALSE}
# Convert non-numeric values to 4 and the column to numeric
vornamen_2023$Anzahl <- ifelse(vornamen_2023$Anzahl == "4 oder weniger", 4, as.numeric(vornamen_2023$Anzahl))

vornamen_2022$Anzahl <- ifelse(vornamen_2022$Anzahl == "4 oder weniger", 4, as.numeric(vornamen_2022$Anzahl))
```

### c) 

```{r}
# Calculate the total number of babies born in Munich in 2023 and 2022
total_babies_2023 <- sum(vornamen_2023$Anzahl)
total_babies_2022 <- sum(vornamen_2022$Anzahl)
```

The baby-boom was bigger in 2022.

### d) 

```{r}
# Add a new column 'year' to both datasets
vornamen_2022$year <- 2023
vornamen_2023$year <- 2022

# Print the datasets to verify the changes
head(vornamen_2023)
head(vornamen_2022)
```

### e) 

```{r}
# Combine both datasets into one
combined_data <- bind_rows(vornamen_2023, vornamen_2022)

# Print the combined dataset
head(combined_data)
```

### f) 

```{r}         
# Group the data by name and sum the counts
popular_names <- combined_data %>%
  group_by(Vorname) %>%
  summarise(Total_Count = sum(Anzahl)) %>%
  arrange(desc(Total_Count))

# Print out the top 10 names for both years in a nicely formatted table
cat("\nTable: Top 10 Most Popular Names Across 2022 and 2023\n")
print(popular_names[1:10, ], row.names = FALSE)
```

## Exercise 4: Open Analysis

### c) 

-   Dataset Name: Indicators for "What is PPP?" - World Bank
-   Link: <https://github.com/owid/owid-datasets/tree/master/datasets/Indicators%20for%20!What%20is%20PPP!%20%20-%20World%20Bank#indicators-for-what-is-ppp----world-bank>

### d) 

**Research Question**: How does the Price Level Ratio (PLR) affect the discrepancy between GDP per capita (PPP) and GDP per capita (USD) across countries?

**Rationale**: This question explores the impact of cost of living on the perceived economic output per individual, providing insights into economic well-being across different countries.

### e) 

```{r}
# Load the dataset in R
PLR_GDPcp_1990_2015 <- read_csv("DATA/PLR_GDPcp_1990_2015.csv")

# View the data structure
head(PLR_GDPcp_1990_2015)
```

```{r}
# Standardize the column names to snake_case
PLR_GDPcp_1990_2015 <- PLR_GDPcp_1990_2015 %>%
  clean_names() 

# Abbreviate the column names
PLR_GDPcp_1990_2015 <- PLR_GDPcp_1990_2015 %>%
  rename(
    plr = price_level_ratio_of_ppp_conversion_factor_gdp_to_market_exchange_rate_world_bank,
    gdp_pc_ppp = gdp_per_capita_ppp_int_adjusted_world_bank,
    gdp_pc_usd = gdp_per_capita_us_market_exchange_world_bank
  ) 
```

```{r}
# Check for missing values
summary(PLR_GDPcp_1990_2015)

# Remove rows with missing values
PLR_GDPcp_2015 <- na.omit(PLR_GDPcp_1990_2015)
```

```{r}
# Filter out rows where price level ratio is greater than 1
higher_lc_2015 <- PLR_GDPcp_2015 %>% 
  filter(plr > 1)

print(higher_lc_2015) # Countries of higher living costs in 2015
```

The table indicates that goods and services were relatively more expensive in these countries compared to the United States back in 2015. 

However, this does not directly imply a higher inflation rate of the year. To examine if there was a higher inflation rate, we need to take a closer look at the differences between GDP per capita (PPP) and GDP per capita (USD).

```{r}
# Compute the difference between GDP per capita (PPP) and GDP per capita (USD)
PLR_GDPcp_2015 <- PLR_GDPcp_2015 %>%
  mutate(gdp_diff = gdp_pc_ppp - gdp_pc_usd)

high_inflated_2015 <- PLR_GDPcp_2015 %>%
  filter(gdp_diff < 0)

print(high_inflated_2015)
```

The table shows these countries experienced a high inflation back in 2015.

```{r}
# Calculate correlation
correlation <- cor(higher_lc_2015$plr, high_inflated_2015$gdp_diff)

# Print correlation
print(correlation)
```
The correlation between PLR and the GDP disparity is -0.9859214, indicating a strong positive correlation. In this case, as PLR increases, the GDP disparity tends to widen.

### f) 

```{r, fig.cap="Relationship between Price Level Ratio and GDP Disparity"}
# Create a scatter plots
ggplot(high_inflated_2015, aes(x = plr, y = gdp_diff)) +
  geom_point() +
  labs(x = "Price Level Ratio", y = "GDP Disparity")
```

